GeoSPARQL 1.1: an almost decadal update to the most important geospatial LOD standard

### 2021-03-12 manuscript.tex
Update on Overleaf.

\begin{itemize}
    \item[$\ast$] \textbf{1.1}: extensions that are fully compatable with GeoSPARQL 1.0
    \item[$\ast$] \textbf{1.2}: fully or mostly compatable extensions but which are larger additions to the standard's conceptual coverage
    \item[$\ast$] \textbf{2.0}: a future GeoSPARQL that might be quite different and partly incompatable with GeoSPARQL 1.0
\end{itemize}

@@

\section{Updates in GeoSPARQL 1.1}\label{sec:newfeatures}
So far (as of June, 2020) the GeoSPARQL SWG has triaged changed requests into GeoSPARQL 1.1, 1.2 \$ 2.0 releases and has addressed
many 1.1 requests. Here we report only on those 1.1 requests. This section describes some of the areas updated in GeoSAPRQL 1.1
and the following section foreshadows likely 1.2 and 2.0 updates.

@@

The profile declaration for GeosPARQL 1.0 will be published by the OGC as a stand-alone resource sometime in early 2021 along with some 
updated GeoSPARQL 1.0 resources. The profile declaration for GeosPARQL 1.1 will be published at the same time as all, or most, of the 
1.1 releases' updated resources, currently expected in mid-2021. The 1.1 releases' resources are:

>>>>

\begin{itemize}
    \item[$\ast$] \textbf{1.1}: extensions that are fully compatible with GeoSPARQL 1.0
    \item[$\ast$] \textbf{1.2}: fully or mostly compatible extensions but which are larger additions to the standard's conceptual coverage
    \item[$\ast$] \textbf{2.0}: a future GeoSPARQL that might be quite different and partly incompatible with GeoSPARQL 1.0
\end{itemize}

@@

\section{Updates in GeoSPARQL 1.1}\label{sec:newfeatures}
So far (as of June, 2020) the GeoSPARQL SWG has triaged changed requests into GeoSPARQL 1.1, 1.2 \$ 2.0 releases and has addressed
many 1.1 requests. Here we report only on those 1.1 requests. This section describes some of the areas updated in GeoSPARQL 1.1
and the following section foreshadows likely 1.2 and 2.0 updates.

@@

The profile declaration for GeoSPARQL 1.0 will be published by the OGC as a stand-alone resource sometime in early 2021 along with some 
updated GeoSPARQL 1.0 resources. The profile declaration for GeoSPARQL 1.1 will be published at the same time as all, or most, of the 
1.1 releases' updated resources, currently expected in mid-2021. The 1.1 releases' resources are:
